End-User Software Customization by Direct Manipulation of Tabular Data

### 2020-08-15 paper.tex
new abstract, new diff

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{Data-Driven Customization of Web Applications}

@@

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  Customizing software should be as easy as using it. But most
  customization methods require a dramatic shift, from using a GUI to
  writing scripts in a programming language.

>>>>

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{End-User Software Customization by Direct Manipulation of Tabular
Data}

@@

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  Customizing software should be as easy as using it. But most
  customization methods require a dramatic shift from using a GUI to
  writing customization scripts in a programming language.
